Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-07-01 supplement/06_bat_data.Rmd

# filter for hour between 8pm and 5am
data_residence = atl_filter_covariates(
  data = data_residence,
  filters = "hour > 20 | hour < 5"
)
```

@@

# get mean residence time per id
data_residence[, list(mean_residence = mean(resTime),
                      sd_residence = sd(resTime)), by = "TAG"]

# get mean residence time for all bats pooled
data_residence[, list(mean_residence = mean(resTime),
                      sd_residence = sd(resTime))]

@@

# exclude roost
patch_summary = patch_summary[x_median > 254000, ]

# get mean and sd of duration in patches
patch_summary[, list(mean_duration = mean(duration / 60), 
                     sd_duration = sd(duration / 60))]

# assign night id
patch_summary[, c("hour", "day") := list(
  data.table::hour(as.POSIXct(time_start, origin = "1970-01-01")),
  data.table::mday(as.POSIXct(time_start, origin = "1970-01-01")))]

@@

# get total foraging time
foraging_proportion = patch_summary[, list(
  time_total_forage = (max(time_end) - min(time_start)) / 60, 
  time_forage_site = sum(duration / 60)),
  by = c("id", "night")
  ]

# get proporion of foraging that is at a foraging site
foraging_proportion[, list(
  mean_foraging_prop = mean(time_forage_site / time_total_forage),
  sd_foraging_prop = sd(time_forage_site / time_total_forage)
)]

```

>>>>

# filter for hour between 8pm and 5am
data_residence <- atl_filter_covariates(
  data = data_residence,
  filters = "hour > 20 | hour < 5"
)
```

@@

# get mean residence time per id
data_residence[, list(
  mean_residence = mean(resTime),
  sd_residence = sd(resTime)
), by = "TAG"]

# get mean residence time for all bats pooled
data_residence[, list(
  mean_residence = mean(resTime),
  sd_residence = sd(resTime)
)]

@@

# exclude roost
patch_summary <- patch_summary[x_median > 254000, ]

# get mean and sd of duration in patches
patch_summary[, list(
  mean_duration = mean(duration / 60),
  sd_duration = sd(duration / 60)
)]

# assign night id
patch_summary[, c("hour", "day") := list(
  data.table::hour(as.POSIXct(time_start, origin = "1970-01-01")),
  data.table::mday(as.POSIXct(time_start, origin = "1970-01-01"))
)]

@@

# get total foraging time
foraging_proportion <- patch_summary[, list(
  time_total_forage = (max(time_end) - min(time_start)) / 60,
  time_forage_site = sum(duration / 60)
),
by = c("id", "night")
]

# get proporion of foraging that is at a foraging site
foraging_proportion[, list(
  mean_foraging_prop = mean(time_forage_site / time_total_forage),
  sd_foraging_prop = sd(time_forage_site / time_total_forage)
)]
```
